Revision 2: Responses to Reviewers Round 2

### 2018-09-24 jfs_submission/paper-pre-submission-revision-2/Responses-round2.Rmd
inserted replies for Reviewer 1 and editor in the responses document.

1.  Headers are included in the abstract and they do not need to be.

2.  Several references include the DOI and year, volume page citations.  Currently we only need the latter if that is available.  Please correct.

3.  Reference 4 is a URL and when checked it indicated that it was no linger updated.  It also did not take an interested reader to the PCST report.  Please use a different reference

4.  Reference 9 is another URL and my check indicated that the page could not be found.  Please correct.

5.  Please follow the formats included in the Information for Authors and abbreviate the journal titles according to Index Medicus

@@

@@

@@

@@

>>>>

1.  Headers are included in the abstract and they do not need to be. *Done*

2.  Several references include the DOI and year, volume page citations.  Currently we only need the latter if that is available.  Please correct. *Done*

3.  Reference 4 is a URL and when checked it indicated that it was no linger updated.  It also did not take an interested reader to the PCST report.  Please use a different reference. *Done*

4.  Reference 9 is another URL and my check indicated that the page could not be found.  Please correct. *Done*

5.  Please follow the formats included in the Information for Authors and abbreviate the journal titles according to Index Medicus *Done*

@@

*Thank you, we have incorporated this change*

@@

*Thank you, we have changed the grammar and incorporated this change*

@@

*We are happy that we could clarify this*

@@

*Thanks a lot for pointing this out, we have made the changes in the paper reflecting this*
